### 2020-06-02 report/sections/server/node.tex
Report: notes on part 1
Report: add figures to Node chapter

\chapter{\fancyname{NodeMPST}: Back-End Session Type Web Development}

@@

\begin{itemize}
\item callbacks => type aliases for each state (handler)
\item need a way for the runtime to distinguish between states
\item attempt at using conditional types, but because they handle conditional union types in a distributed way (give example), cannot be statically typed
\item alternative => use discriminated union by wrapping in an Implementation class
\item all non-terminal states will `return' the successor implementation -- very difficult to resolve in the type-checker in the runtime (give example of what it may look like) -- solve by giving each state implementation the `advance' function to respect the event-driven nature of everything, so they can call it on completion
\item visualise the interaction between runtime and states as a sequence diagram for message passing
\end{itemize}

@@

@@

>>>>

\chapter{\fancyname{NodeMPST}: Back-End Session Type Web Development}
\label{chap:node}

In this chapter, 
we \dots

@@

\begin{itemize}
\item callbacks -- type aliases for each state (handler)
\item need a way for the runtime to distinguish between states
\item attempt at using conditional types, but because they handle conditional union types in a distributed way (give example), cannot be statically typed
\item alternative -- use discriminated union by wrapping in an Implementation class
\item all non-terminal states will `return' the successor implementation -- very difficult to resolve in the type-checker in the runtime (give example of what it may look like) -- solve by giving each state implementation the `advance' function to respect the event-driven nature of everything, so they can call it on completion
\item visualise the interaction between runtime and states as a sequence diagram for message passing
\end{itemize}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{NodeRuntimeEFSM}
\captionof{figure}{Informal Abstraction of EFSM Execution for
Server Endpoints}
\label{fig:noderuntimeefsm}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.8\textwidth}
\centering
\includegraphics[width=\textwidth]{NodeRuntimeReceive2}
\caption{Message processed before transitioning to receive state}
\label{subfig:nodereceivemsgfirst}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.8\textwidth}
\centering
\includegraphics[width=\textwidth]{NodeRuntimeReceive1}
\caption{Message processed after transitioning to receive state}
\label{subfig:nodereceivehandlefirst}
\end{subfigure}
\captionof{figure}{Possible Orderings for Handling Message Event and Preparing
Receive State}
\label{fig:nodereceivecompare}
\end{figure}
